\documentclass[18pt]{article}
%\usepackage[singlespacing]{setspace}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage[letterpaper, total={7in, 10in}]{geometry}

\setlength\parindent{0pt}
\thispagestyle{empty}
\titlespacing\subsubsection{0pt}{10pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\section{0pt}{18pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\providecommand{\tightlist}{
    \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}
}
\providecommand{\datetable}[2]{
    \begin{tabular*}{\textwidth}{@{}r @{\extracolsep{\fill}} l}
        #1 & #2
    \end{tabular*}
}

\begin{document}

  \section*{Isaac B Goss}\label{isaac-b-goss}
    ibg4@pitt.edu \textbar{} (412) 478 - 3219 \textbar{} Pittsburgh, PA \textbar{} isaacgoss.com
    
    \hrule
    
    \subsection*{Education}\label{education}
        \begin{itemize}[label={}]
        \item \datetable{
            \textbf{University of Pittsburgh} \textbar{} 
            Pittsburgh, PA \textbar{} 
            GPA: 3.24 / 4.0
        }{
            May 2018
        }
        \begin{itemize}[ topsep=0pt]\tightlist
          \item Bachelor of Science in Computer Engineering
          \item Minor in Mathematics
        \end{itemize}
        \item \textbf{Relevant Courses}
            \begin{itemize}[label={}, topsep=0pt]
                \item
                Senior Design,
                Operating Systems,
                Cyber-Physical Systems,
                Software Engineering,
                Algorithm Design,
                Compiler Design,
                Combinatorics,
                Computer Architecture,
                Advanced Digital Design,
                % Formal Methods in Computer Science,
                Graph Theory,\\
                Algorithm Implementation,
                System Software
                % Abstract Algebra
                % Probability \& Statistics,
                % Computer Organization,
                % Linear Algebra,
                % Analysis and Design of Microelectronics,
                % Data Structures,
                % Digital Circuits Lab,
                % Theoretical Math,
                % Differential Equations,
                % Digital Logic,
                % Linear Circuits
            \end{itemize}
        \end{itemize}
    
      
    \subsection*{Experience}\label{experience}
        \begin{itemize}[label={}]
        \item \datetable{
            \textbf{University of Pittsburgh} \textbar{} Pittsburgh, PA
        }{Aug 2017 - Present}
        \begin{itemize}[topsep=0pt]
            \item Teaching Assistant: Digital Systems Lab \& Advanced Digital Design
        \end{itemize}
    
        \item \datetable{
            \textbf{Center for High-Performance and Re-configurable Computing} \textbar{} Pittsburgh, PA
        }{May 2017 - Aug 2017}
        \begin{itemize}[topsep=0pt]\tightlist
          \item Research Intern
          \item Investigate trade-offs for embedded sensor networks.
          \item Designed hardware design simulation workflows.
      	\end{itemize}
      
        \item \datetable{
            \textbf{North American MH Registry} 
            \textbar{} Pittsburgh, PA
        }{Nov 2015 - May 2016}
        \begin{itemize}[topsep=0pt]\tightlist
          \item Intern/Programmer
          \item Design web-based data collection forms
          \item Assist in transition to new database (Python transformation tools)
        \end{itemize}

        \item \datetable{
            \textbf{University of Pittsburgh} \textbar{} 
            Greensburg, PA
        }{Dec 2014 - May 2015}
        \begin{itemize}[topsep=0pt]
            \item Mathematics Tutor: Calculus 1, 2, 3, and Physics
        \end{itemize}
        \end{itemize}
      
    \subsection*{Tools}\label{languages}
    \begin{description}\tightlist
        \item[Proficient:] Java,
        C,
        Python,
        VHDL,
        % HTML \& CSS,
        % Markdown,
        git,
        GitHub,
        Unix,
        make,
        regex,
        \LaTeX,
        Javadoc,
        % Catch,
        FPGA
        \item[Learning:] C++,
        % Haskell,
        Rust,
        OpenCV,
        Flask,
        Heroku,
        % bash scripting,
        JUnit,
        Gradle,
        TravisCI,
        JFlex,
        JavaCUP
    \end{description}


    \subsection*{Projects: github.com/iggy14750}\label{projects}
    \begin{itemize}[label={}]\tightlist
        
        \item \datetable{\textbf{ParkPal}}{Jan 2018 - April 2018}
        \begin{itemize}\tightlist
            \item System to display currently open parallel parking spaces.
            \item Embedded platform with camera and WiFi modules watching street.
            \item Server accepts new images, uses computer vision to find open spaces.
        \end{itemize}

        \item \datetable{\textbf{Simulation for Hardware Design}}
        {May 2017 - Aug 2017}
        \begin{itemize}\tightlist
            \item Researched and developed techniques for simulating full systems.
            \item Test-benches written in HDL to drive system, and verify behavior.
            \item Bus-functional models in place of CPU and software.
        \end{itemize}
        
        \item \datetable{\textbf{Nonstandard Template Library}}
        {May 2017 - Present}
        \begin{itemize}\tightlist
            \item Implementation of some data structures and algorithms in C++
            \item Goals are to learn C++, TDD, and review those DS and algos.
        \end{itemize}
            
        \item \datetable{\textbf{MIPS CPU}}{Jan 2017 - April 2017}
        \begin{itemize}\tightlist
            \item 5-Stage Harvard pipeline, with full forwarding, and hazard detection.
            \item Constructed from stratch, only using VHDL primitives.
            \item Built with HDL Designer; simulated using ModelSim.
        \end{itemize}
      
        % \item \datetable{Graph Theory}{Jan 2017 - Apr 2017}
        % \begin{itemize}\tightlist
        %     \item Several assignments in Graph Theory, written up in \LaTeX.
        % \end{itemize}
      
        % \item \datetable{\textbf{Algorithm Projects}}{Aug 2016 - Dec 2016}
        % \begin{itemize}\tightlist
        %     \item Several small applications which exercise algorithmic concepts.
        %     \item Such as using priority queues to organize apt listings.
        % \end{itemize}
            
        \item \datetable{\textbf{Instalight}}{Jan 2016}
        \begin{itemize}\tightlist
            \item Hackathon project which displayed arbitrary strings as Morse code.
            \item Worked on Twitter scraper, sent tweet to be displayed.
        \end{itemize}
        
        \item \datetable{\textbf{The Mathematics of the RSA Cipher}}{Dec 2015}
        \begin{itemize}\tightlist
            \item Describes the motivation and mathematical basis of the RSA cypher.
            \item Includes a proof of Euler's Theorem (of modular exponents).
        \end{itemize}
  \end{itemize}
    
\end{document}
